Titeln på avhandlingens språk

### 2022-11-26 body/part1/overview.tex
scope

\todo[inline]{
    Methodology

    Study by example, human subject research, and modeling.

    Empirical research.

    Include testbeds!
}

\section{Contributions of this thesis}

@@

\begin{contributions}
    \begin{enumerate}[
            before = \leavevmode%\vspace{-.5\baselineskip}
        ]
        \item\label{item:contrib:methodology} A methodological approach to studying system responsiveness versus resource consumption trade-offs in \ac{WCA}.
        This approach is based on the emulation of the client-side workload, while maintaining the \emph{real} server-side process as well as network stack.
        \item In conjunction with the aforementioned methodology, a tool (EdgeDroid) for the emulation of human behavior in \ac{WCA}.
              This tool implements the first ever parametrizable model of human behavior for these applications using empirical data collected from a series of human-subject experiments.
        \item A characterization of the effects of individual personality differences in human responses to reduced system responsiveness in interactive systems such as \acl{WCA}.
              In particular, this thesis presents novel evidence for the modulating properties of \emph{neuroticism} on the reaction to increased delay in these systems.
        \item An preliminary, yet novel exploration of the implications of realistic modeling of human timings in \ac{WCA} applications for their optimization potential.
              \item\label{item:contrib:methodology:ncs} An extension of the methodology described in \cref{item:contrib:methodology} towards \acp{NCS}.
        \item A novel tool, CLEAVE, for the emulation of \acp{NCS} on edge infrastructure.
              This tool has been designed from the ground-up to be edge-native, implemented using widely-adopted technologies in the disciplines of cloud and edge computing.
        \item Finally, a software framework for the management and automation of the testbeds required for the methodology described in \cref{item:contrib:methodology,item:contrib:methodology:ncs}.
    \end{enumerate}
\end{contributions}

>>>>

\todo[inline]{
    Methodology: a system of methods used in a particular area of study or activity.
}

\section{Scope of this thesis}

We study in this thesis a methodological approach to studying system responsiveness versus resource consumption trade-offs in edge-bound feedback-loop systems such as \ac{WCA} and \ac{NCS}.
This approach is based on the emulation of the client-side workload, while maintaining the \emph{real} server-side process as well as network stack.
We validate this methodology by example, presenting a deep exploration of its implementation and applications in the context of \acl{WCA}, and a initial, more shallow foray into its applications in the context of \ac{NCS}.

More specifically, in \cref{paper:Olguin:DemoScaling2018,paper:Olguin:EdgeDroid2019} we introduce this methodology for \ac{WCA}.
\cref{paper:Olguin:DemoScaling2018} presents a short, high level overview of this methodological approach, in particular making very straightforward assumptions about human behavior in \ac{WCA} applications.
\cref{paper:Olguin:EdgeDroid2019} extends the discussion from \cref{paper:Olguin:DemoScaling2018}, providing more details on the implementation of the necessary measurement framework and the tooling employed, as well as on the assumptions that were made about human behavior and reactions.
We assume in these works a human which is impervious to poor system performance, and suffers no annoyance, fatigue, frustration, nausea or other shortcomings of real human users.
This results in a model of a user who responds in a precisely reproducible and deterministic manner to the same system stimulus every time.
\cref{paper:Olguin:EdgeDroid2019} furthermore presents the first empirical results obtained with our methodological approach, providing thus an initial validation of its utility for research.

In that context, we present several ancillary sub-contributions.
The first of these corresponds to  a tool (EdgeDroid) for the emulation of human behavior in \ac{WCA}.
This tool corresponds to a key enabler of our main contribution, as it implements the first ever parametrizable model of human behavior for these applications using empirical data collected from a series of human-subject experiments.
Furthermore, as part of the ground-laying work for this model, we present a first-ever characterization of the effects of individual personality differences in human responses to reduced system responsiveness in interactive systems such as \acl{WCA}.
In particular, this thesis presents novel evidence for the modulating properties of \emph{neuroticism} on the reaction to increased delay in these systems.

@@

\begin{contributions}
    \begin{enumerate}[
            before = \leavevmode%\vspace{-.5\baselineskip}
        ]
        \item\label{item:contrib:methodology} 
        \item In conjunction with the aforementioned methodology,
        \item A 
        \item An preliminary, yet novel exploration of the implications of realistic modeling of human timings in \ac{WCA} applications for their optimization potential.
              \item\label{item:contrib:methodology:ncs} An extension of the methodology described in \cref{item:contrib:methodology} towards \acp{NCS}.
        \item A novel tool, CLEAVE, for the emulation of \acp{NCS} on edge infrastructure.
              This tool has been designed from the ground-up to be edge-native, implemented using widely-adopted technologies in the disciplines of cloud and edge computing.
        \item Finally, a software framework for the management and automation of the testbeds required for the methodology described in \cref{item:contrib:methodology,item:contrib:methodology:ncs}.
    \end{enumerate}
\end{contributions}
